Coronal Fourier power spectra: implications for coronal seismology and coronal heating

### 2014-10-07 tex/paper1/paper1.tex
fiddling around with fugure 4 plots, and a small change to allow the plot captions to be shown on the one page
should be some inconsequential changes
beginning revision 2 edits - all minor
completed second reply to referee

\documentclass[onecolumn]{emulateapj}
%\documentclass[preprint]{aastex}
\usepackage{graphicx}
\usepackage{color}
\usepackage{multirow}
%\usepackage{showkeys}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage{wasysym}
%\usepackage{subfigure}
\usepackage{verbatim}

@@

@@

\title{Coronal Fourier power spectra: implications for coronal
  seismology and coronal heating.}

@@

  {\bf The dynamics of regions of the solar corona are investigated
    using AIA 171\AA\ and 193\AA\ data.  The coronal emission from the
    quiet Sun, coronal loop footprints, coronal moss, and from above a
    sunspot is studied.  It is shown that the \mFpa\ in these regions
    can be described by a \PL\ at lower frequencies that tails to flat
    spectrum at higher frequencies, plus a Gaussian-shaped
    contribution that varies depending on the region studied. This
    Fourier spectral shape is in contrast to the commonly-held
    assumption that coronal time-series are well described by the sum
    of a long time-scale background trend plus Gaussian-distributed
    noise, with some specific locations also showing an oscillatory
    signal.  The implications of this discovery to the field of
    coronal seismology and the automated detections of oscillations
    are discussed.  The \PL\ contribution to the shape of the Fourier
    power spectrum is interpreted as being due to the summation of a
    distribution of exponentially decaying emission events along the
    line of sight.}  This is consistent with the idea that the solar
  atmosphere is heated everywhere by small energy deposition events.
\end{abstract}

@@

\section{Introduction}\label{sec:int}
Coronal seismology is the study of oscillatory phenomena in the solar
corona.  First suggested by \cite{1970PASJ...22..341U}, the practice
of coronal seismology attempts to locate oscillatory phenomena in the
solar corona, identify the wave modes present, and then use
theoretical descriptions of those wave modes to infer the physical
conditions of the solar corona.  The practical application of coronal
seismological ideas began in earnest with observations of wave modes
{\bf described in \cite{1998ApJ...501L.217D} and
  \cite{1999SoPh..186..207B} from data captured by Extreme Ultraviolet
  Telescope (EIT, \citealp{1995SoPh..162..291D}) on board the Solar and Heliospheric
  Observatory (SOHO, \citealp{1995SoPh..162....1D}), and also by
  \citep{1999ApJ...520..880A} using data from the Transition Region
  and Coronal Explorer (TRACE, \citealp{1999SoPh..187..229H}).  Since these initial works,
  many papers have been published describing oscillatory phenomena in
  the corona and their interpretation in terms of theoretically known
  wave modes.  The review articles \cite{lrsp-2005-3} and
  \cite{2012RSPTA.370.3193D} refer to many more articles on both
  observational and theoretical coronal seismology}.

@@

The relative scarcity of observations of coronal oscillations has
prompted efforts to create automated oscillation detection algorithms.
The need for an automated oscillation detection algorithm has been
exacerbated by the large and rapidly growing amount of AIA data.
There have been several attempts at designing such algorithms.
\cite{2004SoPh..223....1D} describe the design of an automated
oscillation-detection algorithm based on wavelet analysis. The
algorithm finds significant wave packets ranging from single to
multiple wave cycles in duration, by a wavelet power/confidence level
comparison against the null hypothesis that a given time series is
Gaussian-distributed noise.  Pixels with significant oscillatory
content are grouped manually.  \cite{2007SoPh..241..397N} take a
similar approach, using a thresholded fast Fourier transform to find
locations in TRACE data that may support an oscillatory signal. The
threshold level is defined as three to four times the average fast
Fourier transform (FFT) power; if the maximum FFT power is above this
level then the frequency at which that power occurs is assumed to be
real. \cite{2010SoPh..264..403I} assume that an oscillatory signal is
present in each location in the datacube and then use a Bayesian-based
treatment to calculate the probability that the frequency has a
particular value.  This algorithm relies on subtracting a background
trend from the time-series being tested, and assumes that the noise is
Gaussian distributed.

The above algorithms precipitate detections based on the strength of
the signal of an oscillation on a pixel by pixel basis, and then group
these pixels together using some set of criteria.  The automated
detection algorithm of \cite{2008SoPh..248..395S} begins by
identifying candidate oscillatory regions as those whose time-series
of emission show a high variance \citep{2003SoPh..213..103G} (under
the implicit assumption that the time-series has an approximately
constant mean value).  Detections are based on wavelet filtering of
these regions in all three dimensions of the data cube simultaneously,
with the implicit assumption that the noise is Gaussian-distributed.
{\bf The algorithm of \cite{2008SoPh..252..321M} differs from the
  previous algorithms: it begins by Fourier transforming the entire
  data cube, and calculating the coherence of neighboring pixels in
  narrow frequency bands, and filtering the results. The null
  hypothesis here is that pairs of time series that have low coherence
  can be rejected as being part of an oscillatory group.  This method
  uses a symmetric filter to estimate the coherence, in that
  oscillatory power from either side of the central search frequency
  contributes the same weight to the final result.  There is an
  implicit assumption here that the power on either side of the
  central search frequency is approximately the same.  In this
  algorithm, the spatial extent of the coherence of the oscillatory
  signal is the key identifier of a wave process.}

All these detections algorithms, and many detections in the literature
make either the explicit or implicit assumption that the observed
time-series consists of a background trend of some kind and
(approximately) Gaussian-distributed noise which must be taken in to
account in order to test for the presence of an oscillatiory signal
{\bf \cite{2004SoPh..223....1D, 2007SoPh..241..397N,
    2008SoPh..248..395S, 2010SoPh..264..403I, 2013SoPh..286..405C}.}
{\bf However, two recent papers cast doubt on this assumption.
  \cite{2014AA...563A...8A} integrate emission over small portions of
  active regions and the quiet Sun as observed in the 195\AA\ passband
  images from EIT and show that the resulting time-series has an
  approximate \PL\ \Fps\ over the frequency range 0.01 - 1 mHz.
  \citet{gupta2014} showed \PL\ \PA\ in the intensity at six single
  points in AIA 171\AA\ coronal plumes extending over the frequency range
  $0.3\rightarrow 4.0$ mHz.}

{\bf The aim of this paper is to investigate the nature of the Fourier
  power spectrum in regions of interest to coronal seismology, to look
  for evidence that the above assumption is appropriate.}  The nature
of coronal emission has implications for coronal seismology, and may
be indicative of the nature of the fundamental energy deposition that
keeps the corona hot.  Section \ref{sec:obs} describes the
observations used, while Section \ref{sec:anal} describes the method
of analysis employed and presents the results.  Section
\ref{sec:discuss} discusses the implication of these results for
coronal seismology and the heating of the solar atmosphere.  Section
\ref{sec:conc} summarizes the discussion and outlines future work.

\section{Observations}\label{sec:obs}
{\bf Data from the Atmospheric Imaging Assembly (AIA,
  \citealp{2012SoPh..275...17L}) on board the Solar Dynamics
  Observatory (SDO, \citealp{2012SoPh..275....3P}) are used.}  AIA
observes images of the Sun in multiple wavebands simultaneously and
continuously, at high cadence (12 seconds) and at high spatial
resolution (0.6 arcseconds per pixel).  These data enable detailed
comparisons between phenomena observed in multiple wavebands, and are
therefore ideal for assessing the frequency content of the solar
atmosphere.  The data was acquired using the Lockheed Martin Solar
Astrophysics cutout service at {\it
http://lmsal.com/get\_aia\_data/}.  Six hours of image data in
the time range 2012-09-23 00:00 - 06:00 UT, at the full 12 second
cadence, in the 171\AA\ and 193\AA\ wavebands is used.  These
wavebands were selected because previous studies in similar wavebands
(TRACE 171\AA\ and 193\AA) show the presence of coronal oscillations.
{\bf The selected area covers a single $\beta\gamma$ active region,
  NOAA AR 11575}.  This area was selected for two reasons.  First, it
is quiescent in that there were no X-ray flares or other large-scale
disturbances (for example, filament eruptions or rearrangments of long
bright coronal loops) over the spatial extent of the cutout within the
time range (Figure \ref{fig:loc171193}).  Therefore, any variations in
the plasma properties cannot be ascribed to large-scale disturbances.
Second, the selected cutout region contains a sunspot, and sunspots
are known to be locations over which three minute oscillations have
been detected by other instruments \citep{2002A&A...387L..13D}.

The data was prepared for analysis using the SolarSoft / IDL routines
READ\_SDO and AIA\_PREP.  These procedures convert the downloaded
level 1.0 FITS cutout files to level 1.5 FITS files.  This involves
translating, scaling and rotating the images so they have the same
sun-center, image scale with solar north in the same direction.  All
further processing from this point was performed in the SunPy 0.4
(http://www.sunpy.org) data analysis environment.  Images were
de-rotated to compensate for solar rotation, based on the center of
the field of view of each image.  After de-rotation, each image layer
was coaligned with a reference layer, defined to be half way through
the dataset, in this case at approximately 03:00 UT (Figure
\ref{fig:loc171193}).  This process is required since the solar
de-rotation function used does not fully compensate for all the solar
rotation. {\bf Coalignment was implemented using a template matching
  technique \citep{lewis1995fast} implemented by the {\it
    scikit-image} \citep{Vanderwalt2014} routine {\it
    match\_template}.  A rectangular template sub-image with sides one
  half the size (in pixels) of the reference layer is defined.  The
  coalignment algorithm finds the location of the best match of this
  template with each layer.  The image layer is then shifted (using
  sub-pixel shifts) according to the location of the best match of the
  template with the image.  This process removes residual bulk motions
  of the images.}

\section{Analysis}\label{sec:anal}
We wish to analyze the frequency content of these resulting datacubes
as a function of spatial location.  Four locations were chosen in the
data representing four different types of physical locations in the
solar atmosphere.  These were a quiet Sun region, a region that lies
on top of a sunspot, a footpoint region, and a coronal moss region.
Figure \ref{fig:loc171193} shows the location of the regions on sample
images from the time range considered. {\bf These locations, selected
  by visual inspection, were chosen because they are representative of
  commonly observed structures in the corona.  Further,
  oscillatory power has been identified previously over sunspots and
  loop footpoints \citep{2002A&A...387L..13D} and moss structures
  \citep{2003ApJ...595L..63D}.  A quiet Sun region is also included
  for comparison.}
\begin{figure}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
}
\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
  193\AA, overlaid on sample images taken halfway through the six hour
  span used to form the time-series analyzed.  The spatial extent of
  the data is (-501'', -138'') in the x-direction, and (-80'', 107'')
  in the y-direction, in heliocentric cartesian co-ordinates.  The
  images show NOAA AR 11575 and some surrounding area.}
\label{fig:loc171193}
\end{figure}

@@

\begin{figure}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
}
\caption{{\bf The proportion of the number of pixels in each image
    that have a given Fourier power at some sample Fourier
    frequencies.  The left hand column gives results for AIA 171\AA,
    and the right hand column, AIA 193\AA.  Regions are indicated in
    each plot title.}}
\label{fig:dist171193}
\end{figure}
Figure \ref{fig:dist171193} shows the probability distribution of the
Fourier power of the pixels in each region at five selected
frequencies, for all the pixels in each region.  These distributions
are centrally peaked, show a slightly heavier tail towards lower
Fourier powers (negative skew), are slightly broader when compared to
a Gaussian distribution, and are all unimodal.  These observations
guide the choice of how to average the \PS\ over each of the selected
region.  The nature of these distributions suggest that the arithmetic
mean of the Fourier power is biased by the very largest powers.
Therefore, the mean value of the logarithm of the Fourier power is a
better description of the range of values in the data (this is
equivalent to the geometric mean of the Fourier power).  The \PA\ used
below are calculated from the mean value of the logarithm of the
Fourier power.

\begin{figure}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\caption{Geometric mean of the \protect\Fpa\ (black solid line) in
  each of the four regions studied in AIA 171\AA\ (left column) and
  AIA 193\AA\ (right column).  Also shown are the posterior mean fits
  for model $M_{1}$ and $M_{2}$ (blue and red lines respectively; see
  Section \ref{sec:anal} and Appendix \ref{sec:app:ind} for more
  detail).  The AIC describing the preference for model over the other
  is also indicated in each plot.  The reduced $chi^{2}_{r}$ statistic
  for Model 1 and Model 2 are given. The two components to Model 2,
  $P_{1}(\nu)$ and $G(\nu)$ are also shown in green; the location of
  the maximum of the $G(\nu)/P_{1}(\nu)$ ratio is indicated by the
  green dotted line.  Model fit parameter values and their 68\%
  credible intervals are quoted in Table \ref{tab:parameters}.}
\label{fig:fit171193}
\end{figure}

@@

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  \cite{2003ApJ...595L..63D} show that TRACE
171\AA\ (TRansition Region And Coronal Explorer) time-series of bright
upper transition region emission above active region plage (also known
as moss) is a source of wavelet power. Periods of significant wavelet
power are found in the range 200 to 600 seconds, and typically persist
for 4–7 cycles.  Later work by \cite{2005ApJ...624L..61D} suggested
that spicule flux tubes tilted with respect to the solar surface
provide a mechanism by which oscillatory power from lower in the
atmosphere may be channeled to upper portions of the atmosphere.  This
suggests that a second model $M_{2}$ for the \Fps\ in regions should
be considered.  The second model $M_{2}$ has two contributions to the
overall \Fps; a background power-law of the form of $P_{1}$, and a
contribution that is more localized, $G(\nu)$.  The model is given by
\begin{equation}
\label{eqn:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\delta^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions (Figure
\ref{fig:fit171193}), and compared to decide which model best
describes the data. A Bayesian probability based parameter estimation
and model fitting is implemented.  This approach was chosen for its
flexibility and consistent error estimation properties
\citep{2013ApJ...769...89I}.  The details of the model fitting process
are described in Appendix \ref{sec:app:ind}.  The position of $G(\nu)$ is
restricted by permitting $\beta$ to vary in the range $0.1-10$ mHz
only.  This restriction, which is imposed in the fitting process (see
Appendix \ref{sec:app:ind}), arises from the observations of
significant wavelet power in the period range 200 - 600 seconds as
found by \cite{2003ApJ...595L..63D}.

>>>>

%\documentclass[onecolumn]{emulateapj}
%\documentclass[twocolumn]{aastex}
\documentclass[referee]{aastex}
\usepackage{graphicx}
\usepackage{color}
\usepackage{multirow}
\usepackage{setspace}

%\usepackage{showkeys}
\usepackage{epsfig}
\usepackage{natbib}
\usepackage{wasysym}
%\usepackage{subfigure}
\usepackage{verbatim}

@@

\newcommand{\BF}{ }

@@

\title{Coronal Fourier power spectra: implications for coronal
  seismology and coronal heating}

@@

  {\BF The dynamics of regions of the solar corona are investigated
    using {\bf Atmospheric Imaging Assembly (AIA)} 171\AA\ and
    193\AA\ data.  The coronal emission from the quiet Sun, coronal
    loop footprints, coronal moss, and from above a sunspot is
    studied.  It is shown that the \mFpa\ in these regions can be
    described by a \PL\ at lower frequencies that tails to flat
    spectrum at higher frequencies, plus a Gaussian-shaped
    contribution that varies depending on the region studied. This
    Fourier spectral shape is in contrast to the commonly-held
    assumption that coronal time-series are well described by the sum
    of a long time-scale background trend plus Gaussian-distributed
    noise, with some specific locations also showing an oscillatory
    signal.  The implications of this discovery to the field of
    coronal seismology and the automated detections of oscillations
    are discussed.  The \PL\ contribution to the shape of the Fourier
    power spectrum is interpreted as being due to the summation of a
    distribution of exponentially decaying emission events along the
    line of sight.}  This is consistent with the idea that the solar
  atmosphere is heated everywhere by small energy deposition events.
\end{abstract}

@@

\section{Introduction}\label{sec:int}
Coronal seismology is the study of oscillatory phenomena in the solar
corona.  First suggested by \cite{1970PASJ...22..341U}, the practice
of coronal seismology attempts to locate oscillatory phenomena in the
solar corona, identify the wave modes present, and then use
theoretical descriptions of those wave modes to infer the physical
conditions of the solar corona.  The practical application of coronal
seismological ideas began in earnest with observations of wave modes
{\BF described in \cite{1998ApJ...501L.217D} and
  \cite{1999SoPh..186..207B} from data captured by Extreme Ultraviolet
  Telescope (EIT, \citealp{1995SoPh..162..291D}) on board the Solar and Heliospheric
  Observatory (SOHO, \citealp{1995SoPh..162....1D}), and also by
  \citep{1999ApJ...520..880A} using data from the Transition Region
  and Coronal Explorer (TRACE, \citealp{1999SoPh..187..229H}).  Since these initial works,
  many papers have been published describing oscillatory phenomena in
  the corona and their interpretation in terms of theoretically known
  wave modes.  The review articles \cite{lrsp-2005-3} and
  \cite{2012RSPTA.370.3193D} refer to many more articles on both
  observational and theoretical coronal seismology}.

@@

The relative scarcity of observations of coronal oscillations has
prompted efforts to create automated oscillation detection algorithms.
The need for an automated oscillation detection algorithm has been
exacerbated by the large and rapidly growing amount of {\bf Solar
  Dynamics Observatory (SDO, \citealp{2012SoPh..275....3P})
  Atmospheric Imaging Assembly (AIA, \citealp{2012SoPh..275...17L})}
data.  There have been several attempts at designing such algorithms.
\cite{2004SoPh..223....1D} describe the design of an automated
oscillation-detection algorithm based on wavelet analysis. The
algorithm finds significant wave packets ranging from single to
multiple wave cycles in duration, by a wavelet power/confidence level
comparison against the null hypothesis that a given time series is
Gaussian-distributed noise.  Pixels with significant oscillatory
content are grouped manually.  \cite{2007SoPh..241..397N} take a
similar approach, using a thresholded fast Fourier transform to find
locations in TRACE data that may support an oscillatory signal. The
threshold level is defined as three to four times the average fast
Fourier transform (FFT) power; if the maximum FFT power is above this
level then the frequency at which that power occurs is assumed to be
real. \cite{2010SoPh..264..403I} assume that an oscillatory signal is
present in each location in the datacube and then use a Bayesian-based
treatment to calculate the probability that the frequency has a
particular value.  This algorithm relies on subtracting a background
trend from the time-series being tested, and assumes that the noise is
Gaussian distributed.

The above algorithms precipitate detections based on the strength of
the signal of an oscillation on a pixel by pixel basis, and then group
these pixels together using some set of criteria.  The automated
detection algorithm of \cite{2008SoPh..248..395S} begins by
identifying candidate oscillatory regions as those whose time-series
of emission show a high variance \citep{2003SoPh..213..103G} (under
the implicit assumption that the time-series has an approximately
constant mean value).  Detections are based on wavelet filtering of
these regions in all three dimensions of the data cube simultaneously,
with the implicit assumption that the noise is Gaussian-distributed.
{\BF The algorithm of \cite{2008SoPh..252..321M} differs from the
  previous algorithms: it begins by Fourier transforming the entire
  data cube, and calculating the coherence of neighboring pixels in
  narrow frequency bands, and filtering the results. The null
  hypothesis here is that pairs of time series that have low coherence
  can be rejected as being part of an oscillatory group.  This method
  uses a symmetric filter to estimate the coherence, in that
  oscillatory power from either side of the central search frequency
  contributes the same weight to the final result.  There is an
  implicit assumption here that the power on either side of the
  central search frequency is approximately the same.  In this
  algorithm, the spatial extent of the coherence of the oscillatory
  signal is the key identifier of a wave process.}

All these detections algorithms, and many detections in the literature
make either the explicit or implicit assumption that the observed
time-series consists of a background trend of some kind and
(approximately) Gaussian-distributed noise which must be taken in to
account in order to test for the presence of an oscillatiory signal
{\bf \citep{2004SoPh..223....1D, 2007SoPh..241..397N,
    2008SoPh..248..395S, 2010SoPh..264..403I, 2013SoPh..286..405C}.}
{\BF However, two recent papers cast doubt on this assumption.
  \cite{2014AA...563A...8A} integrate emission over small portions of
  active regions and the quiet Sun as observed in the 195\AA\ passband
  images from EIT and show that the resulting time-series has an
  approximate \PL\ \Fps\ over the frequency range 0.01 - 1 mHz.
  \citet{gupta2014} showed \PL\ \PA\ in the intensity at six single
  points in AIA 171\AA\ coronal plumes extending over the frequency range
  $0.3\rightarrow 4.0$ mHz.}

{\BF The aim of this paper is to investigate the nature of the Fourier
  power spectrum in regions of interest to coronal seismology, to look
  for evidence that the above assumption is appropriate.}  The nature
of coronal emission has implications for coronal seismology, and may
be indicative of the nature of the fundamental energy deposition that
keeps the corona hot.  Section \ref{sec:obs} describes the
observations used, while Section \ref{sec:anal} describes the method
of analysis employed and presents the results.  Section
\ref{sec:discuss} discusses the implication of these results for
coronal seismology and the heating of the solar atmosphere.  Section
\ref{sec:conc} summarizes the discussion and outlines future work.

\section{Observations}\label{sec:obs}
{\bf AIA} observes images of the Sun in multiple wavebands
simultaneously and continuously, at high cadence (12 seconds) and at
high spatial resolution (0.6 arcseconds per pixel).  These data enable
detailed comparisons between phenomena observed in multiple wavebands,
and are therefore ideal for assessing the frequency content of the
solar atmosphere.  {\bf AIA} data was acquired using the Lockheed Martin
Solar Astrophysics cutout service at {\it
  http://lmsal.com/get\_aia\_data/}.  Six hours of image data in the
time range 2012-09-23 00:00 - 06:00 UT, at the full 12 second cadence,
in the 171\AA\ and 193\AA\ wavebands is used.  These wavebands were
selected because previous studies in similar wavebands (TRACE
171\AA\ and 193\AA) show the presence of coronal oscillations.  {\BF
  The selected area covers a single $\beta\gamma$ active region, NOAA
  AR 11575}.  This area was selected for two reasons.  First, it is
quiescent in that there were no X-ray flares or other large-scale
disturbances (for example, filament eruptions or rearrangments of long
bright coronal loops) over the spatial extent of the cutout within the
time range (Figure \ref{fig:loc171193}).  Therefore, any variations in
the plasma properties cannot be ascribed to large-scale disturbances.
Second, the selected cutout region contains a sunspot, and sunspots
are known to be locations over which three minute oscillations have
been detected by other instruments \citep{2002A&A...387L..13D}.

The data was prepared for analysis using the SolarSoft / IDL routines
READ\_SDO and AIA\_PREP.  These procedures convert the downloaded
level 1.0 FITS cutout files to level 1.5 FITS files.  This involves
translating, scaling and rotating the images so they have the same
sun-center, image scale with solar north in the same direction.  All
further processing from this point was performed in the SunPy 0.4
(http://www.sunpy.org) data analysis environment.  Images were
de-rotated to compensate for solar rotation, based on the center of
the field of view of each image.  After de-rotation, each image layer
was coaligned with a reference layer, defined to be half way through
the dataset, in this case at approximately 03:00 UT (Figure
\ref{fig:loc171193}).  This process is required since the solar
de-rotation function used does not fully compensate for all the solar
rotation. {\BF Coalignment was implemented using a template matching
  technique \citep{lewis1995fast} implemented by the {\it
    scikit-image} \citep{Vanderwalt2014} routine {\it
    match\_template}.  A rectangular template sub-image with sides one
  half the size (in pixels) of the reference layer is defined.  The
  coalignment algorithm finds the location of the best match of this
  template with each layer.  The image layer is then shifted (using
  sub-pixel shifts) according to the location of the best match of the
  template with the image.  This process removes residual bulk motions
  of the images.}

\section{Analysis}\label{sec:anal}
We wish to analyze the frequency content of these resulting datacubes
as a function of spatial location.  Four locations were chosen in the
data representing four different types of physical locations in the
solar atmosphere.  These were a quiet Sun region, a region that lies
on top of a sunspot, a footpoint region, and a coronal moss region.
Figure \ref{fig:loc171193} shows the location of the regions on sample
images from the time range considered. {\BF These locations, selected
  by visual inspection, were chosen because they are representative of
  commonly observed structures in the corona.  Further,
  oscillatory power has been identified previously over sunspots and
  loop footpoints \citep{2002A&A...387L..13D} and moss structures
  \citep{2003ApJ...595L..63D}.  A quiet Sun region is also included
  for comparison.}
\begin{figure}
\centerline{
\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
}
\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
  193\AA, overlaid on sample images taken halfway through the six hour
  span used to form the time-series analyzed.  The spatial extent of
  the data is (-501'', -138'') in the x-direction, and (-80'', 107'')
  in the y-direction, in heliocentric cartesian co-ordinates.  The
  images show NOAA AR 11575 and some surrounding area.}
\label{fig:loc171193}
\end{figure}

@@

\begin{figure}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
}
\caption{{\BF The proportion of the number of pixels in each image
    that have a given Fourier power at some sample Fourier
    frequencies.  The left hand column gives results for AIA 171\AA,
    and the right hand column, AIA 193\AA.  Regions are indicated in
    each plot title.}}
\label{fig:dist171193}
\end{figure}
Figure \ref{fig:dist171193} shows the probability distribution of the
Fourier power of the pixels in each region at five selected
frequencies, for all the pixels in each region.  These distributions
are centrally peaked, show a slightly heavier tail towards lower
Fourier powers (negative skew), are slightly broader when compared to
a Gaussian distribution, and are all unimodal.  These observations
guide the choice of how to average the \PS\ over each of the selected
region.  The nature of these distributions suggest that the arithmetic
mean of the Fourier power is biased by the very largest powers.
Therefore, the mean value of the logarithm of the Fourier power is a
better description of the range of values in the data (this is
equivalent to the geometric mean of the Fourier power).  The \PA\ used
below are calculated from the mean value of the logarithm of the
Fourier power.

\begin{figure}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\centerline{
\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
}
\begin{singlespace}
 \caption{Geometric mean of the \protect\Fpa\ (black
    solid line) in each of the four regions studied in AIA
    171\AA\ (left column) and AIA 193\AA\ (right column).  Also shown
    are the posterior mean fits for model $M_{1}$ and $M_{2}$ (blue
    and red lines respectively; see Section \ref{sec:anal} and
    Appendix \ref{sec:app:ind} for more detail).  The AIC describing
    the preference for model over the other is also indicated in each
    plot.  The reduced $chi^{2}_{r}$ statistic for Model 1 and Model 2
    are given. The two components to Model 2, $P_{1}(\nu)$ and
    $G(\nu)$ are also shown in green; the location of the maximum of
    the $G(\nu)/P_{1}(\nu)$ ratio is indicated by the green dotted
    line.  Model fit parameter values and their 68\% credible
    intervals are quoted in Table \ref{tab:parameters}.}
\end{singlespace}
\label{fig:fit171193}

\end{figure}

@@

The moss results for 171\AA\ and 193\AA\ are notably different from
the other results.  In comparison to the general trend observed in
other regions, there appears to be excess Fourier power in the range
1-10 mHz.  \cite{2003ApJ...595L..63D} show that {\bf TRACE}
171\AA\ time-series of bright upper transition region emission above
active region plage (also known as moss) is a source of wavelet
power. Periods of significant wavelet power are found in the range 200
to 600 seconds, and typically persist for 4–7 cycles.  Later work by
\cite{2005ApJ...624L..61D} suggested that spicule flux tubes tilted
with respect to the solar surface provide a mechanism by which
oscillatory power from lower in the atmosphere may be channeled to
upper portions of the atmosphere.  This suggests that a second model
$M_{2}$ for the \Fps\ in regions should be considered.  The second
model $M_{2}$ has two contributions to the overall \Fps; a background
power-law of the form of $P_{1}$, and a contribution that is more
localized, $G(\nu)$.  The model is given by
\begin{equation}
\label{eqn:pwrlawbump}
\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
\end{equation}
where the localized contribution is described by
\begin{equation}
\label{eqn:bump}
G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\delta^{2}}\right].
\end{equation}
Both these models are fit to the geometrically averaged Fourier power
spectrum in both wavelengths and in all four regions (Figure
\ref{fig:fit171193}).  {\bf Model fitting and parameter estimation are
  implemented using a Bayesian probability based approach.}  This
approach was chosen for its flexibility and consistent error
estimation properties \citep{2013ApJ...769...89I}.  The details of the
model fitting process are described in Appendix \ref{sec:app:ind}.
The position of $G(\nu)$ is restricted by permitting $\beta$ to vary
in the range $0.1-10$ mHz only.  This restriction, which is imposed in
the fitting process (see Appendix \ref{sec:app:ind}), arises from the
observations of significant wavelet power in the period range 200 -
600 seconds as found by \cite{2003ApJ...595L..63D}.  {\bf After this
  fitting process is complete, the models are compared to decide which
  model best describes the data.  The details of the model comparison
  process are described in the following section.}
